\section{Possible Solutions}
If any user is a victim of misinformation, it can be assumed that he has exposed himself to an unofficially accredited source of information. He has consumed information that has not been verified, and this has probably induced him to make erroneous decisions as a result of this false information. But it's very important to note that,\emph{under most circumstances, fake news come to users when they are in a relaxed mode for information consumption instead of a critical-thinking mode for work or for study. \cite{kanohWhyPeopleBelieve2018}.}This means that many people are just vulnerable to information, and don't approach what they perceive with a critical mind. Criticism means questioning the source, making a logical analysis of what you perceive as information, both visually and in terms of content. This situation reveals an alarming reality about how our psychology can influence the reception of information. If a person is in a relaxed state, such as eating or drinking, he or she is more vulnerable to passively absorbing information without questioning its veracity. It therefore becomes clear that one of the first methods of combating disinformation in an environment polluted by deepFakes would be to have everyone think critically when confronted with information.

on the other hand, The ethical aspect of AI should be taken into consideration. \emph{  AI continues demonstrating its positive impact on society while sometimes with ethically questionable consequences. Not doing AI responsibly is starting to have devastating effect on humanity, not only on data protection, privacy, and bias but also on labor rights and climate justice. Building and maintaining public trust in AI has been identified as the key to successful and sustainable innovation . Thus, the issue of ethical AI or responsible AI has gathered high-level attention. Nearly one hundred principles and guidelines for ethical AI have been issued by private companies, research institutions, and public organizations  and some consensus around high-level principles has emerged.\cite{zhuAIEthicsOperationalizing2022}}